\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\title{View problem}
\author{USACO Contest: JAN21 Contest - Bronze Division}
\date{\today}

\begin{document}

\maketitle

\section*{Problem Statement}

A little known fact about cows is that they have their own version of the
alphabet, the "cowphabet".  It consists of the 26 letters 'a' through 'z', but
when a cow speaks the cowphabet, she lists these letters in a specific ordering
that might be different from the order 'abcdefghijklmnopqrstuvwxyz' we are used to
hearing.

To pass the time, Bessie the cow has been humming the cowphabet over and  over
again, and Farmer John is curious how many times she's hummed it.

Given a lowercase string of letters that Farmer John has heard Bessie say,
compute the minimum number of times Bessie must have hummed the entire cowphabet
in order for Farmer John to have heard the given string. Farmer John isn't
always paying attention to what Bessie hums, and so he might have missed some of
the letters that Bessie has hummed.  The string you are told consists of just
the letters that he remembers hearing.

INPUT FORMAT (input arrives from the terminal / stdin):
The first line of input contains the 26 lowercase letters 'a' through 'z' in the
order they appear in the cowphabet.  The next line contains the string  of
lowercase letters that Farmer John heard Bessie say.  This string has length at
least $1$ and at most $1000$.

OUTPUT FORMAT (print output to the terminal / stdout):
Print the minimum number of times Bessie must have hummed the entire cowphabet.

SAMPLE INPUT:
abcdefghijklmnopqrstuvwxyz
mood
SAMPLE OUTPUT: 
3

In this example, the cowphabet is ordered the same as the normal alphabet.

Bessie must have hummed the cowphabet at least three times. It is possible for
Bessie to have only hummed the cowphabet three times, and for Farmer John to
have heard the letters in uppercase as denoted below.


abcdefghijklMnOpqrstuvwxyz
abcdefghijklmnOpqrstuvwxyz
abcDefghijklmnopqrstuvwxyz

SCORING:
In test cases 2-5, the cowphabet is the same as the normal alphabet.Test cases 6-10 satisfy no additional constraints.


Problem credits: Nick Wu



\section*{Input Format}
OUTPUT FORMAT (print output to the terminal / stdout):Print the minimum number of times Bessie must have hummed the entire cowphabet.SAMPLE INPUT:abcdefghijklmnopqrstuvwxyz
moodSAMPLE OUTPUT:3In this example, the cowphabet is ordered the same as the normal alphabet.Bessie must have hummed the cowphabet at least three times. It is possible for
Bessie to have only hummed the cowphabet three times, and for Farmer John to
have heard the letters in uppercase as denoted below.abcdefghijklMnOpqrstuvwxyz
abcdefghijklmnOpqrstuvwxyz
abcDefghijklmnopqrstuvwxyzSCORING:In test cases 2-5, the cowphabet is the same as the normal alphabet.Test cases 6-10 satisfy no additional constraints.Problem credits: Nick Wu

\section*{Output Format}
SAMPLE INPUT:abcdefghijklmnopqrstuvwxyz
moodSAMPLE OUTPUT:3In this example, the cowphabet is ordered the same as the normal alphabet.Bessie must have hummed the cowphabet at least three times. It is possible for
Bessie to have only hummed the cowphabet three times, and for Farmer John to
have heard the letters in uppercase as denoted below.abcdefghijklMnOpqrstuvwxyz
abcdefghijklmnOpqrstuvwxyz
abcDefghijklmnopqrstuvwxyzSCORING:In test cases 2-5, the cowphabet is the same as the normal alphabet.Test cases 6-10 satisfy no additional constraints.Problem credits: Nick Wu

\section*{Sample Input}
\begin{verbatim}
abcdefghijklmnopqrstuvwxyz
mood
\end{verbatim}

\section*{Sample Output}
\begin{verbatim}
3

In this example, the cowphabet is ordered the same as the normal alphabet.Bessie must have hummed the cowphabet at least three times. It is possible for
Bessie to have only hummed the cowphabet three times, and for Farmer John to
have heard the letters in uppercase as denoted below.abcdefghijklMnOpqrstuvwxyz
abcdefghijklmnOpqrstuvwxyz
abcDefghijklmnopqrstuvwxyzSCORING:In test cases 2-5, the cowphabet is the same as the normal alphabet.Test cases 6-10 satisfy no additional constraints.Problem credits: Nick Wu

Bessie must have hummed the cowphabet at least three times. It is possible for
Bessie to have only hummed the cowphabet three times, and for Farmer John to
have heard the letters in uppercase as denoted below.abcdefghijklMnOpqrstuvwxyz
abcdefghijklmnOpqrstuvwxyz
abcDefghijklmnopqrstuvwxyzSCORING:In test cases 2-5, the cowphabet is the same as the normal alphabet.Test cases 6-10 satisfy no additional constraints.Problem credits: Nick Wu

abcdefghijklMnOpqrstuvwxyz
abcdefghijklmnOpqrstuvwxyz
abcDefghijklmnopqrstuvwxyzSCORING:In test cases 2-5, the cowphabet is the same as the normal alphabet.Test cases 6-10 satisfy no additional constraints.Problem credits: Nick Wu

abcdefghijklMnOpqrstuvwxyz
abcdefghijklmnOpqrstuvwxyz
abcDefghijklmnopqrstuvwxyz

SCORING:In test cases 2-5, the cowphabet is the same as the normal alphabet.Test cases 6-10 satisfy no additional constraints.Problem credits: Nick Wu
\end{verbatim}

\section*{Solution}


\section*{Problem URL}
https://usaco.org/index.php?page=viewproblem2&cpid=1083

\section*{Source}
USACO JAN21 Contest, Bronze Division, Problem ID: 1083

\end{document}
