\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\title{View problem}
\author{USACO Contest: DEC18 Contest - Silver Division}
\date{\today}

\begin{document}

\maketitle

\section*{Problem Statement}

Farmer John is hosting a new bovine grass-eating convention at his farm!

Cows from all over the world are arriving at the local airport to attend the
convention and eat grass. Specifically, there are $N$ cows arriving at the
airport ($1 \leq N \leq 10^5$) and cow $i$ arrives at time $t_i$
($0 \leq t_i \leq 10^9$). Farmer John has arranged $M$ ($1 \leq M \leq 10^5$)
buses to transport the cows from the airport. Each bus can hold up to $C$
cows in it ($1 \leq C \leq N$). Farmer John is waiting with the buses at the
airport and would like to assign the arriving cows to the buses. A bus can leave
at the time when the last cow on it arrives. Farmer John wants to be a good host
and so does not want to keep the arriving cows waiting at the airport too long.
What is the smallest  possible value of the maximum waiting time of any one
arriving cow if Farmer John coordinates his buses optimally? A cow’s waiting
time is the difference between her arrival time and the departure of her
assigned bus.

It is guaranteed that $MC \geq N$.

INPUT FORMAT (file convention.in):
The first line contains three space separated integers $N$, $M$, and $C$. The
next line contains $N$ space separated integers representing the arrival time of
each cow.

OUTPUT FORMAT (file convention.out):
Please write one line containing the optimal minimum maximum waiting time for
any one arriving cow.

SAMPLE INPUT:
6 3 2
1 1 10 14 4 3
SAMPLE OUTPUT: 
4

If the two cows arriving at time 1 go in one bus, cows arriving at times 3 and 4
in the second, and cows arriving at times 10 and 14 in the third, the longest
time a cow has to wait is 4 time units (the cow arriving at time 10 waits from
time 10 to time 14).


Problem credits: Grace Cai



\section*{Input Format}
OUTPUT FORMAT (file convention.out):Please write one line containing the optimal minimum maximum waiting time for
any one arriving cow.SAMPLE INPUT:6 3 2
1 1 10 14 4 3SAMPLE OUTPUT:4If the two cows arriving at time 1 go in one bus, cows arriving at times 3 and 4
in the second, and cows arriving at times 10 and 14 in the third, the longest
time a cow has to wait is 4 time units (the cow arriving at time 10 waits from
time 10 to time 14).Problem credits: Grace Cai

\section*{Output Format}
SAMPLE INPUT:6 3 2
1 1 10 14 4 3SAMPLE OUTPUT:4If the two cows arriving at time 1 go in one bus, cows arriving at times 3 and 4
in the second, and cows arriving at times 10 and 14 in the third, the longest
time a cow has to wait is 4 time units (the cow arriving at time 10 waits from
time 10 to time 14).Problem credits: Grace Cai

\section*{Sample Input}
\begin{verbatim}
6 3 2
1 1 10 14 4 3
\end{verbatim}

\section*{Sample Output}
\begin{verbatim}
4

If the two cows arriving at time 1 go in one bus, cows arriving at times 3 and 4
in the second, and cows arriving at times 10 and 14 in the third, the longest
time a cow has to wait is 4 time units (the cow arriving at time 10 waits from
time 10 to time 14).Problem credits: Grace Cai

Problem credits: Grace Cai

Problem credits: Grace Cai
\end{verbatim}

\section*{Solution}


\section*{Problem URL}
https://usaco.org/index.php?page=viewproblem2&cpid=858

\section*{Source}
USACO DEC18 Contest, Silver Division, Problem ID: 858

\end{document}
