\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\title{View problem}
\author{USACO Contest: DEC19 Contest - Silver Division}
\date{\today}

\begin{document}

\maketitle

\section*{Problem Statement}

Farmer John's cows have recently become fans of playing a simple number game
called "FizzBuzz".  The rules of the game are simple: standing in a circle, the
cows sequentially count upward from one, each cow saying a single number when it
is her turn.  If a cow ever reaches a multiple of 3, however, she should say
"Fizz" instead of that number.  If a cow reaches a multiple of 5, she should say
"Buzz" instead of that number.  If a cow reaches a multiple of 15, she should
say "FizzBuzz" instead of that number.  A transcript of the first part of a game
is therefore:

1, 2, Fizz, 4, Buzz, Fizz, 7, 8, Fizz, Buzz, 11, Fizz, 13, 14, FizzBuzz, 16

Having a slightly more limited vocabulary, the version of FizzBuzz played by the
cows involves saying "Moo" instead of Fizz, Buzz, and FizzBuzz.  The beginning
of the cow version of the game is therefore

1, 2, Moo, 4, Moo, Moo, 7, 8, Moo, Moo, 11, Moo, 13, 14, Moo, 16

Given $N$ ($1 \leq N \leq 10^9$), please determine the $N$th number spoken in
this game.

SCORING
Test cases 2-5 satisfy $N\le 10^6.$ 

INPUT FORMAT (file moobuzz.in):
The input consists of a single integer, $N$.

OUTPUT FORMAT (file moobuzz.out):
Please print out the $N$th number spoken during the game.

SAMPLE INPUT:
4
SAMPLE OUTPUT: 
7

The 4th number spoken is 7.  The first 4 numbers spoken are 1, 2, 4, 7, since we
skip over any time a cow says "Moo".


Problem credits: Brian Dean



\section*{Input Format}
OUTPUT FORMAT (file moobuzz.out):Please print out the $N$th number spoken during the game.SAMPLE INPUT:4SAMPLE OUTPUT:7The 4th number spoken is 7.  The first 4 numbers spoken are 1, 2, 4, 7, since we
skip over any time a cow says "Moo".Problem credits: Brian Dean

\section*{Output Format}
SAMPLE INPUT:4SAMPLE OUTPUT:7The 4th number spoken is 7.  The first 4 numbers spoken are 1, 2, 4, 7, since we
skip over any time a cow says "Moo".Problem credits: Brian Dean

\section*{Sample Input}
\begin{verbatim}
4
\end{verbatim}

\section*{Sample Output}
\begin{verbatim}
7

The 4th number spoken is 7.  The first 4 numbers spoken are 1, 2, 4, 7, since we
skip over any time a cow says "Moo".Problem credits: Brian Dean

Problem credits: Brian Dean

Problem credits: Brian Dean
\end{verbatim}

\section*{Solution}


\section*{Problem URL}
https://usaco.org/index.php?page=viewproblem2&cpid=966

\section*{Source}
USACO DEC19 Contest, Silver Division, Problem ID: 966

\end{document}
