\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\title{View problem}
\author{USACO Contest: FEB19 Contest - Silver Division}
\date{\today}

\begin{document}

\maketitle

\section*{Problem Statement}

A lengthy drought has left Farmer John's $N$ pastures devoid of grass.  However,
with the rainy season arriving soon, the time has come to "revegetate".
In Farmer John's shed, he has two buckets, each with a different type of grass 
seed.  He wants to plant grass in each of his $N$ pastures, choosing exactly
one type of grass to plant in each.

Being a dairy farmer, Farmer John wants to make sure he manages the somewhat
particular dietary needs of his $M$ cows.  Each of his $M$ cows has two favorite 
pastures.  Some of his cows have a dietary restriction that they should only eat
one type of grass consistently --- Farmer John therefore wants to make sure the
same type of grass is planted in the two favorite fields of any such cow.  Other
cows have a very different dietary restriction, requiring them to eat different
types of grass.  For those cows, Farmer John of course wants to make sure their 
two favorite fields contain different grass types.

Please help Farmer John determine the number of different ways he can plant 
grass in his $N$ pastures.

INPUT FORMAT (file revegetate.in):
The first line of input contains $N$ ($2 \leq N \leq 10^5$) and $M$
($1 \leq M \leq 10^5$). Each of the next $M$ lines contains a character
that is either 'S' or 'D', followed by two integers in the
range $1 \ldots N$, describing the pair of pastures that are the two favorites
for one of Farmer John's cows.  If the character is 'S', this line represents
a cow that needs the same type of grass in its two favorite pastures.  If
the character is 'D', the line represents a cow that needs different grass
types.

OUTPUT FORMAT (file revegetate.out):
Output the number of ways Farmer John can plant grass in his $N$ pastures.
Please write your answer in binary.

SAMPLE INPUT:
3 2
S 1 2
D 3 2
SAMPLE OUTPUT: 
10


Problem credits: Dhruv Rohatgi and Brian Dean



\section*{Input Format}
OUTPUT FORMAT (file revegetate.out):Output the number of ways Farmer John can plant grass in his $N$ pastures.
Please write your answer in binary.SAMPLE INPUT:3 2
S 1 2
D 3 2SAMPLE OUTPUT:10Problem credits: Dhruv Rohatgi and Brian Dean

\section*{Output Format}
SAMPLE INPUT:3 2
S 1 2
D 3 2SAMPLE OUTPUT:10Problem credits: Dhruv Rohatgi and Brian Dean

\section*{Sample Input}
\begin{verbatim}
3 2
S 1 2
D 3 2
\end{verbatim}

\section*{Sample Output}
\begin{verbatim}
10

Problem credits: Dhruv Rohatgi and Brian Dean

Problem credits: Dhruv Rohatgi and Brian Dean
\end{verbatim}

\section*{Solution}


\section*{Problem URL}
https://usaco.org/index.php?page=viewproblem2&cpid=920

\section*{Source}
USACO FEB19 Contest, Silver Division, Problem ID: 920

\end{document}
