\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\title{View problem}
\author{USACO Contest: OPEN15 Contest - Silver Division}
\date{\today}

\begin{document}

\maketitle

\section*{Problem Statement}

Farmer John has received a shipment of $N$ large hay bales ($1 \le N \le 4000$)
and placed them at various locations along the road leading to his barn.
Unfortunately, he completely forgets that Bessie the cow is out grazing along
the road, and she may now be trapped within the bales!
Each bale $j$ has a size $S_j$ and a distinct position $P_j$ giving its location
along the one-dimensional road.  Bessie the cow starts at some location where
there is no hay bale, and can move around freely along the road, even up to the
position at which a bale is located, but she cannot cross through this position.
As an exception, if she runs in the same direction for $D$ units of distance,
she builds up enough speed to break through and permanently eliminate any hay
bale of size strictly less than $D$.  Of course, after doing this, she
might open up more space to allow her to make a run at other hay bales,
eliminating them as well.  
Bessie can escape to freedom if she can eventually break through either the 
leftmost or rightmost hay bale.  Please compute the total area of the road
consisting of real-valued starting positions from which Bessie cannot escape.
For example, if Bessie cannot escape if she starts between hay bales at 
positions 1 and 5, then these encompass an area of size 4 from which she  cannot
escape.
INPUT FORMAT (file trapped.in):
The first line of input contains $N$.  Each of the next $N$ lines describes a
bale, and contains two integers giving its size and position, each in the range
$1\ldots 10^9$.  

OUTPUT FORMAT (file trapped.out):
Print a single integer, giving the area of the road from which Bessie cannot
escape.

SAMPLE INPUT:5
8 1
1 4
8 8
7 15
4 20
SAMPLE OUTPUT: 14

[Problem credits: Brian Dean, 2015]



\section*{Input Format}
OUTPUT FORMAT (file trapped.out):Print a single integer, giving the area of the road from which Bessie cannot
escape.SAMPLE INPUT:5
8 1
1 4
8 8
7 15
4 20SAMPLE OUTPUT:14[Problem credits: Brian Dean, 2015]

\section*{Output Format}
SAMPLE INPUT:5
8 1
1 4
8 8
7 15
4 20SAMPLE OUTPUT:14[Problem credits: Brian Dean, 2015]

\section*{Sample Input}
\begin{verbatim}
5
8 1
1 4
8 8
7 15
4 20
\end{verbatim}

\section*{Sample Output}
\begin{verbatim}
14

[Problem credits: Brian Dean, 2015]
\end{verbatim}

\section*{Solution}


\section*{Problem URL}
https://usaco.org/index.php?page=viewproblem2&cpid=547

\section*{Source}
USACO OPEN15 Contest, Silver Division, Problem ID: 547

\end{document}
