\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\title{View problem}
\author{USACO Contest: DEC15 Contest - Platinum Division}
\date{\today}

\begin{document}

\maketitle

\section*{Problem Statement}

Farmer John has installed a new system of $N-1$ pipes to transport milk between
the $N$ stalls in his barn ($2 \leq N \leq 50,000$), conveniently numbered
$1 \ldots N$.  Each pipe connects a pair of stalls,  and all stalls are
connected to each-other via paths of pipes.  

FJ is pumping milk between $K$ pairs of stalls ($1 \leq K \leq 100,000$).  For
the $i$th such pair,  you are told two stalls $s_i$ and $t_i$, endpoints of a
path along which milk is being pumped at a unit rate.  FJ is concerned that some
stalls might end up overwhelmed with all the milk being pumped through them,
since a stall can serve as a waypoint along many of the $K$ paths along which
milk is being pumped.  Please help him determine the maximum amount of milk
being pumped through any stall.  If milk is being pumped along a path from $s_i$
to $t_i$, then it counts as being pumped through the endpoint stalls $s_i$ and
$t_i$, as well as through every stall along the path between them.

INPUT FORMAT (file maxflow.in):

The first line of the input contains $N$ and $K$.

The next $N-1$ lines each contain two integers $x$ and $y$ ($x \ne y$) describing a pipe
between stalls $x$ and $y$.

The next $K$ lines each contain two integers $s$ and $t$ describing the endpoint
stalls of a path through  which milk is being pumped.


OUTPUT FORMAT (file maxflow.out):
An integer specifying the maximum amount of milk pumped through any stall in the
barn.


SAMPLE INPUT:
5 10
3 4
1 5
4 2
5 4
5 4
5 4
3 5
4 3
4 3
1 3
3 5
5 4
1 5
3 4

SAMPLE OUTPUT: 
9

Problem credits: Brian Dean



\section*{Input Format}
The next $N-1$ lines each contain two integers $x$ and $y$ ($x \ne y$) describing a pipe
between stalls $x$ and $y$.The next $K$ lines each contain two integers $s$ and $t$ describing the endpoint
stalls of a path through  which milk is being pumped.

The next $K$ lines each contain two integers $s$ and $t$ describing the endpoint
stalls of a path through  which milk is being pumped.

OUTPUT FORMAT (file maxflow.out):An integer specifying the maximum amount of milk pumped through any stall in the
barn.SAMPLE INPUT:5 10
3 4
1 5
4 2
5 4
5 4
5 4
3 5
4 3
4 3
1 3
3 5
5 4
1 5
3 4SAMPLE OUTPUT:9Problem credits: Brian Dean

\section*{Output Format}
SAMPLE INPUT:5 10
3 4
1 5
4 2
5 4
5 4
5 4
3 5
4 3
4 3
1 3
3 5
5 4
1 5
3 4SAMPLE OUTPUT:9Problem credits: Brian Dean

\section*{Sample Input}
\begin{verbatim}
5 10
3 4
1 5
4 2
5 4
5 4
5 4
3 5
4 3
4 3
1 3
3 5
5 4
1 5
3 4
\end{verbatim}

\section*{Sample Output}
\begin{verbatim}
9

Problem credits: Brian Dean
\end{verbatim}

\section*{Solution}


\section*{Problem URL}
https://usaco.org/index.php?page=viewproblem2&cpid=576

\section*{Source}
USACO DEC15 Contest, Platinum Division, Problem ID: 576

\end{document}
