\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\title{View problem}
\author{USACO Contest: DEC17 Contest - Platinum Division}
\date{\today}

\begin{document}

\maketitle

\section*{Problem Statement}

Farmer John's nemesis, Farmer Nhoj, has $N$ cows ($1 \leq N \leq 10^5$),
conveniently numbered $1 \dots N$. They have unexpectedly turned up at Farmer
John's farm, so the unfailingly polite Farmer John is attempting to give them
gifts.

To this end, Farmer John has brought out his infinite supply of gifts, and
Nhoj's cows have queued up in front of him, with cow $1$ at the head of the
queue and cow $N$ at the tail. Farmer John was expecting that at every timestep,
the cow at the head of the queue would take a gift from Farmer John and go to
the tail of the queue.  However, he has just realized that Nhoj's cows are not
that polite!  After receiving her gift, each cow may not go to the tail of the
queue, but rather may cut some number of cows at the tail, and insert herself in
front of them. Specifically, cow $i$ will always cut exactly $c_i$ cows
($0 \leq c_i \leq N-1$).

Farmer John knows that some cows might receive multiple gifts; as he has an
infinite supply, this does not worry him. But he is worried that some cows might
become unhappy if they do not get any gifts.

Help Farmer John find the number of cows who never receive any gifts, no matter
how many gifts are handed out.

INPUT FORMAT (file greedy.in):
The first line contains a single integer, $N$.

The second line contains $N$ space-separated integers $c_1, c_2, \dots, c_N$.


OUTPUT FORMAT (file greedy.out):
Please output the number of cows who cannot receive any gifts.

SAMPLE INPUT:
3
1 2 0
SAMPLE OUTPUT: 
1


Problem credits: Dhruv Rohatgi



\section*{Input Format}
The second line contains $N$ space-separated integers $c_1, c_2, \dots, c_N$.

OUTPUT FORMAT (file greedy.out):Please output the number of cows who cannot receive any gifts.SAMPLE INPUT:3
1 2 0SAMPLE OUTPUT:1Problem credits: Dhruv Rohatgi

\section*{Output Format}
SAMPLE INPUT:3
1 2 0SAMPLE OUTPUT:1Problem credits: Dhruv Rohatgi

\section*{Sample Input}
\begin{verbatim}
3
1 2 0
\end{verbatim}

\section*{Sample Output}
\begin{verbatim}
1

Problem credits: Dhruv Rohatgi

Problem credits: Dhruv Rohatgi
\end{verbatim}

\section*{Solution}


\section*{Problem URL}
https://usaco.org/index.php?page=viewproblem2&cpid=770

\section*{Source}
USACO DEC17 Contest, Platinum Division, Problem ID: 770

\end{document}
