\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\title{View problem}
\author{USACO Contest: FEB25 Contest - Platinum Division}
\date{\today}

\begin{document}

\maketitle

\section*{Problem Statement}


**Note: The time limit for this problem is 3s, 1.5x the default. The memory
limit for this problem is 512MB, twice the default.**
Bessie is taking an $N$-question true or false test ($1\le N\le 2\cdot 10^5$).
For the $i$-th question, she will gain $a_i$ points if she gets it correct, lose
$b_i$ points if she gets it incorrect, or remain even if she does not answer it
($0<a_i,b_i\le 10^9$).

Bessie knows all the answers because she is a smart cow, but worries that Elsie
(who is administering the test) will retroactively change up to $k$ of the
questions after the test such that Bessie does not get those questions correct.

Given $Q$ ($1\le Q\le N+1$) candidate values of $k$ ($0\le k\le N$), determine
the number of points Bessie can guarantee for each $k$, given that she must
answer at least $k$ questions.

INPUT FORMAT (input arrives from the terminal / stdin):
The first line contains $N$ and $Q$.

The next $N$ lines each contain $a_i$ and $b_i$.

The next $Q$ lines each contain a value of $k$. No value of $k$ appears more
than once.

OUTPUT FORMAT (print output to the terminal / stdout):
The answer for each $k$ on a separate line.

SAMPLE INPUT:
2 3
3 1
4 2
2
1
0
SAMPLE OUTPUT: 
-3
1
7

For each value of $k$, it is optimal for Bessie to answer all of the questions.

SCORING:
Inputs 2-4: $N\le 100$Inputs 5-7: $Q\le 10$,
$N\le 2\cdot 10^5$Inputs 7-20: No additional constraints.


Problem credits: Benjamin Qi



\section*{Input Format}
The next $N$ lines each contain $a_i$ and $b_i$.The next $Q$ lines each contain a value of $k$. No value of $k$ appears more
than once.

The next $Q$ lines each contain a value of $k$. No value of $k$ appears more
than once.

OUTPUT FORMAT (print output to the terminal / stdout):The answer for each $k$ on a separate line.SAMPLE INPUT:2 3
3 1
4 2
2
1
0SAMPLE OUTPUT:-3
1
7For each value of $k$, it is optimal for Bessie to answer all of the questions.SCORING:Inputs 2-4: $N\le 100$Inputs 5-7: $Q\le 10$,
$N\le 2\cdot 10^5$Inputs 7-20: No additional constraints.Problem credits: Benjamin Qi

\section*{Output Format}
SAMPLE INPUT:2 3
3 1
4 2
2
1
0SAMPLE OUTPUT:-3
1
7For each value of $k$, it is optimal for Bessie to answer all of the questions.SCORING:Inputs 2-4: $N\le 100$Inputs 5-7: $Q\le 10$,
$N\le 2\cdot 10^5$Inputs 7-20: No additional constraints.Problem credits: Benjamin Qi

\section*{Sample Input}
\begin{verbatim}
2 3
3 1
4 2
2
1
0
\end{verbatim}

\section*{Sample Output}
\begin{verbatim}
-3
1
7

For each value of $k$, it is optimal for Bessie to answer all of the questions.SCORING:Inputs 2-4: $N\le 100$Inputs 5-7: $Q\le 10$,
$N\le 2\cdot 10^5$Inputs 7-20: No additional constraints.Problem credits: Benjamin Qi

SCORING:Inputs 2-4: $N\le 100$Inputs 5-7: $Q\le 10$,
$N\le 2\cdot 10^5$Inputs 7-20: No additional constraints.Problem credits: Benjamin Qi
\end{verbatim}

\section*{Solution}


\section*{Problem URL}
https://usaco.org/index.php?page=viewproblem2&cpid=1502

\section*{Source}
USACO FEB25 Contest, Platinum Division, Problem ID: 1502

\end{document}
