\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\title{View problem}
\author{USACO Contest: FEB20 Contest - Platinum Division}
\date{\today}

\begin{document}

\maketitle

\section*{Problem Statement}

Farmer John's pasture can be represented by a $N\times N$  square grid
$(1\le N\le 300)$ consisting of positions $(i,j)$ for all $1\le i,j\le N$. For
each square of the grid, the corresponding character in the input is equal to
'*' if there exists a single cow at that position and '.' if there does not
exist a cow at that position.

FJ believes that the beauty of his pasture is directly proportional to the
number of triples of cows such that their positions are equidistant from each
other. In other words, they form an equilateral triangle. Unfortunately, it was
only quite recently that FJ realized that since all of his cows are located at
integer coordinates, no beautiful triples can possibly exist if Euclidean
distance is used! Thus, FJ has decided to switch to use "Manhattan" distance
instead. Formally, the Manhattan distance between two positions $(x_0,y_0)$ and
$(x_1,y_1)$ is equal to $|x_0-x_1|+|y_0-y_1|$.

Given the grid representing the positions of the cows, compute the number of
equilateral triples.

SCORING:
There will be fourteen test cases aside from the sample, one for each of
$N\in \{50,75,100,125,150,175,200,225,250,275,300,300,300,300\}.$

INPUT FORMAT (file triangles.in):
The first line contains a single integer $N.$

For each $1\le i\le N,$ line $i+1$ of the input contains a string of length $N$
consisting solely of the characters '*' and '.'. The $j$th character 
describes whether there exists a cow at position $(i,j)$ or not.

OUTPUT FORMAT (file triangles.out):
Output a single integer containing the answer. It can be shown that it fits into
a signed 32-bit integer.

SAMPLE INPUT:
3
*..
.*.
*..
SAMPLE OUTPUT: 
1

There are three cows, and they form an equilateral triple because the Manhattan
distance between each pair of cows is equal to two.


Problem credits: Benjamin Qi



\section*{Input Format}
For each $1\le i\le N,$ line $i+1$ of the input contains a string of length $N$
consisting solely of the characters '*' and '.'. The $j$th character 
describes whether there exists a cow at position $(i,j)$ or not.

OUTPUT FORMAT (file triangles.out):Output a single integer containing the answer. It can be shown that it fits into
a signed 32-bit integer.SAMPLE INPUT:3
*..
.*.
*..SAMPLE OUTPUT:1There are three cows, and they form an equilateral triple because the Manhattan
distance between each pair of cows is equal to two.Problem credits: Benjamin Qi

\section*{Output Format}
SAMPLE INPUT:3
*..
.*.
*..SAMPLE OUTPUT:1There are three cows, and they form an equilateral triple because the Manhattan
distance between each pair of cows is equal to two.Problem credits: Benjamin Qi

\section*{Sample Input}
\begin{verbatim}
3
*..
.*.
*..
\end{verbatim}

\section*{Sample Output}
\begin{verbatim}
1

There are three cows, and they form an equilateral triple because the Manhattan
distance between each pair of cows is equal to two.Problem credits: Benjamin Qi

Problem credits: Benjamin Qi

Problem credits: Benjamin Qi
\end{verbatim}

\section*{Solution}


\section*{Problem URL}
https://usaco.org/index.php?page=viewproblem2&cpid=1021

\section*{Source}
USACO FEB20 Contest, Platinum Division, Problem ID: 1021

\end{document}
