\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\title{View problem}
\author{USACO Contest: JAN22 Contest - Platinum Division}
\date{\today}

\begin{document}

\maketitle

\section*{Problem Statement}

As usual, Bessie the cow is causing trouble in Farmer John's barn. FJ has $N$
($1\leq N \leq 5000$) stacks of haybales. For each $i\in [1,N]$, the $i$th stack
has $h_i$ ($1\le h_i\le 10^9$) haybales. Bessie does not want any haybales to
fall, so the only operation she can perform is as follows:

If two adjacent stacks' heights differ by exactly one, she can move the top
haybale of the taller stack to the shorter stack.

How many configurations are obtainable after performing the above operation
finitely many times, modulo $10^9+7$? Two configurations are considered the same
if, for all $i$, the $i$th stack has the same number of haybales in both.

INPUT FORMAT (input arrives from the terminal / stdin):
The first line contains $T$ ($1\le T\le 10$), the number of independent test
cases, all of which must be solved to solve one input correctly.

Each test case consists of $N$, and then a sequence of $N$ heights. It is
guaranteed that the sum of $N$ over all test cases does not exceed $5000$.

OUTPUT FORMAT (print output to the terminal / stdout):
Please output $T$ lines, one for each test case.

SAMPLE INPUT:
7
4
2 2 2 3
4
3 3 1 2
4
5 3 4 2
6
3 3 1 1 2 2
6
1 3 3 4 1 2
6
4 1 2 3 5 4
10
1 5 6 6 6 4 2 3 2 5
SAMPLE OUTPUT: 
4
4
5
15
9
8
19

For the first test case, the four possible configurations are:

$$(2,2,2,3), (2,2,3,2), (2,3,2,2), (3,2,2,2).$$
For the second test case, the four possible configurations are:

$$(2,3,3,1),(3,2,3,1),(3,3,2,1), (3,3,1,2).$$
SCORING:
Inputs 1-3 satisfy $N\le 10$.Input 4 satisfies $1\le h_i\le 3$ for all $i$.Inputs 5-7 satisfy $|h_i-i|\le 1$ for all $i$.Inputs 8-10 satisfy $1\le h_i\le 4$ for all $i$ and $N\le 100$.Inputs 11-13 satisfy $N\le 100$.Inputs 14-17 satisfy $N\le 1000$.Inputs 18-21 satisfy no additional constraints.


Problem credits: Daniel Zhang



\section*{Input Format}
Each test case consists of $N$, and then a sequence of $N$ heights. It is
guaranteed that the sum of $N$ over all test cases does not exceed $5000$.

OUTPUT FORMAT (print output to the terminal / stdout):Please output $T$ lines, one for each test case.SAMPLE INPUT:7
4
2 2 2 3
4
3 3 1 2
4
5 3 4 2
6
3 3 1 1 2 2
6
1 3 3 4 1 2
6
4 1 2 3 5 4
10
1 5 6 6 6 4 2 3 2 5SAMPLE OUTPUT:4
4
5
15
9
8
19For the first test case, the four possible configurations are:$$(2,2,2,3), (2,2,3,2), (2,3,2,2), (3,2,2,2).$$For the second test case, the four possible configurations are:$$(2,3,3,1),(3,2,3,1),(3,3,2,1), (3,3,1,2).$$SCORING:Inputs 1-3 satisfy $N\le 10$.Input 4 satisfies $1\le h_i\le 3$ for all $i$.Inputs 5-7 satisfy $|h_i-i|\le 1$ for all $i$.Inputs 8-10 satisfy $1\le h_i\le 4$ for all $i$ and $N\le 100$.Inputs 11-13 satisfy $N\le 100$.Inputs 14-17 satisfy $N\le 1000$.Inputs 18-21 satisfy no additional constraints.Problem credits: Daniel Zhang

\section*{Output Format}
SAMPLE INPUT:7
4
2 2 2 3
4
3 3 1 2
4
5 3 4 2
6
3 3 1 1 2 2
6
1 3 3 4 1 2
6
4 1 2 3 5 4
10
1 5 6 6 6 4 2 3 2 5SAMPLE OUTPUT:4
4
5
15
9
8
19For the first test case, the four possible configurations are:$$(2,2,2,3), (2,2,3,2), (2,3,2,2), (3,2,2,2).$$For the second test case, the four possible configurations are:$$(2,3,3,1),(3,2,3,1),(3,3,2,1), (3,3,1,2).$$SCORING:Inputs 1-3 satisfy $N\le 10$.Input 4 satisfies $1\le h_i\le 3$ for all $i$.Inputs 5-7 satisfy $|h_i-i|\le 1$ for all $i$.Inputs 8-10 satisfy $1\le h_i\le 4$ for all $i$ and $N\le 100$.Inputs 11-13 satisfy $N\le 100$.Inputs 14-17 satisfy $N\le 1000$.Inputs 18-21 satisfy no additional constraints.Problem credits: Daniel Zhang

\section*{Sample Input}
\begin{verbatim}
7
4
2 2 2 3
4
3 3 1 2
4
5 3 4 2
6
3 3 1 1 2 2
6
1 3 3 4 1 2
6
4 1 2 3 5 4
10
1 5 6 6 6 4 2 3 2 5
\end{verbatim}

\section*{Sample Output}
\begin{verbatim}
4
4
5
15
9
8
19

For the first test case, the four possible configurations are:$$(2,2,2,3), (2,2,3,2), (2,3,2,2), (3,2,2,2).$$For the second test case, the four possible configurations are:$$(2,3,3,1),(3,2,3,1),(3,3,2,1), (3,3,1,2).$$SCORING:Inputs 1-3 satisfy $N\le 10$.Input 4 satisfies $1\le h_i\le 3$ for all $i$.Inputs 5-7 satisfy $|h_i-i|\le 1$ for all $i$.Inputs 8-10 satisfy $1\le h_i\le 4$ for all $i$ and $N\le 100$.Inputs 11-13 satisfy $N\le 100$.Inputs 14-17 satisfy $N\le 1000$.Inputs 18-21 satisfy no additional constraints.Problem credits: Daniel Zhang

$$(2,2,2,3), (2,2,3,2), (2,3,2,2), (3,2,2,2).$$For the second test case, the four possible configurations are:$$(2,3,3,1),(3,2,3,1),(3,3,2,1), (3,3,1,2).$$SCORING:Inputs 1-3 satisfy $N\le 10$.Input 4 satisfies $1\le h_i\le 3$ for all $i$.Inputs 5-7 satisfy $|h_i-i|\le 1$ for all $i$.Inputs 8-10 satisfy $1\le h_i\le 4$ for all $i$ and $N\le 100$.Inputs 11-13 satisfy $N\le 100$.Inputs 14-17 satisfy $N\le 1000$.Inputs 18-21 satisfy no additional constraints.Problem credits: Daniel Zhang

For the second test case, the four possible configurations are:$$(2,3,3,1),(3,2,3,1),(3,3,2,1), (3,3,1,2).$$SCORING:Inputs 1-3 satisfy $N\le 10$.Input 4 satisfies $1\le h_i\le 3$ for all $i$.Inputs 5-7 satisfy $|h_i-i|\le 1$ for all $i$.Inputs 8-10 satisfy $1\le h_i\le 4$ for all $i$ and $N\le 100$.Inputs 11-13 satisfy $N\le 100$.Inputs 14-17 satisfy $N\le 1000$.Inputs 18-21 satisfy no additional constraints.Problem credits: Daniel Zhang

$$(2,3,3,1),(3,2,3,1),(3,3,2,1), (3,3,1,2).$$SCORING:Inputs 1-3 satisfy $N\le 10$.Input 4 satisfies $1\le h_i\le 3$ for all $i$.Inputs 5-7 satisfy $|h_i-i|\le 1$ for all $i$.Inputs 8-10 satisfy $1\le h_i\le 4$ for all $i$ and $N\le 100$.Inputs 11-13 satisfy $N\le 100$.Inputs 14-17 satisfy $N\le 1000$.Inputs 18-21 satisfy no additional constraints.Problem credits: Daniel Zhang

SCORING:Inputs 1-3 satisfy $N\le 10$.Input 4 satisfies $1\le h_i\le 3$ for all $i$.Inputs 5-7 satisfy $|h_i-i|\le 1$ for all $i$.Inputs 8-10 satisfy $1\le h_i\le 4$ for all $i$ and $N\le 100$.Inputs 11-13 satisfy $N\le 100$.Inputs 14-17 satisfy $N\le 1000$.Inputs 18-21 satisfy no additional constraints.Problem credits: Daniel Zhang
\end{verbatim}

\section*{Solution}


\section*{Problem URL}
https://usaco.org/index.php?page=viewproblem2&cpid=1189

\section*{Source}
USACO JAN22 Contest, Platinum Division, Problem ID: 1189

\end{document}
