\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\title{View problem}
\author{USACO Contest: OPEN20 Contest - Platinum Division}
\date{\today}

\begin{document}

\maketitle

\section*{Problem Statement}

Farmer John has a small field in the shape of an $N$ by $N$ grid
($1 \le N \le 2000$) where the $j$-th square from the left of the $i$-th row
from the top is denoted by $(i,j)$ for all $1 \le i,j \le N$. He is interested
in planting sweet corn and alfalfa in his field. To do so, he needs to install
some special sprinklers.

A sweet corn sprinkler in square $(I,J)$ will sprinkle all squares to the
bottom-left: i.e. $(i,j)$ with $I \le i$ and $j \le J$.

An alfalfa sprinkler in square $(I,J)$ will sprinkle all squares to the
top-right: i.e. $(i,j)$ with $i \le I$ and $J \le j$.

A square sprinkled by one or multiple sweet corn sprinklers can grow sweet corn;
a square sprinkled by one or multiple alfalfa sprinklers can grow alfalfa. But a
square sprinkled by both types of sprinklers (or neither type) can grow nothing.

Help FJ determine the number of ways (modulo $10^9 + 7$) to install sprinklers
in his field, at most one per square, so that every square is fertile (i.e.,
sprinkled by exactly one type of sprinkler).

Some of the squares are already occupied by woolly cows; this doesn't prevent
these squares from being fertile, but no sprinklers can be installed in such
squares.

INPUT FORMAT (file sprinklers2.in):
The first line contains a single integer $N.$

For each $1\le i\le N,$ the $i+1$-st line contains a string of length $N$
denoting the $i$-th row of the grid. Each character of the string is one of 'W'
(indicating a square occupied by a woolly cow), or '.' (unoccupied).

OUTPUT FORMAT (file sprinklers2.out):
Output the remainder when the number of ways to install sprinklers is divided by
$10^9+7.$

SAMPLE INPUT:
2
..
..
SAMPLE OUTPUT: 
28

Here are all fourteen possibilities when sweet corn can grow at $(1,1)$.


CC  .C  CA  CC  .C  CA  CA  C.  CA  C.  CC  .C  CC  .C  
CC, CC, CC, .C, .C, .C, CA, CA, .A, .A, C., C., .., ..

SAMPLE INPUT:
4
..W.
..WW
WW..
...W
SAMPLE OUTPUT: 
2304

This satisfies the constraints for the first subtask described below.

SCORING:
Test cases 3-4 satisfy $N\le 10$ and there are at most ten unoccupied
squares.Test cases 5-9 satisfy $N\le 200$.Test cases 10-16 satisfy no additional constraints.


Problem credits: Benjamin Qi



\section*{Input Format}
For each $1\le i\le N,$ the $i+1$-st line contains a string of length $N$
denoting the $i$-th row of the grid. Each character of the string is one of 'W'
(indicating a square occupied by a woolly cow), or '.' (unoccupied).

OUTPUT FORMAT (file sprinklers2.out):Output the remainder when the number of ways to install sprinklers is divided by
$10^9+7.$SAMPLE INPUT:2
..
..SAMPLE OUTPUT:28Here are all fourteen possibilities when sweet corn can grow at $(1,1)$.CC  .C  CA  CC  .C  CA  CA  C.  CA  C.  CC  .C  CC  .C  
CC, CC, CC, .C, .C, .C, CA, CA, .A, .A, C., C., .., ..SAMPLE INPUT:4
..W.
..WW
WW..
...WSAMPLE OUTPUT:2304This satisfies the constraints for the first subtask described below.SCORING:Test cases 3-4 satisfy $N\le 10$ and there are at most ten unoccupied
squares.Test cases 5-9 satisfy $N\le 200$.Test cases 10-16 satisfy no additional constraints.Problem credits: Benjamin Qi

\section*{Output Format}
SAMPLE INPUT:2
..
..SAMPLE OUTPUT:28Here are all fourteen possibilities when sweet corn can grow at $(1,1)$.CC  .C  CA  CC  .C  CA  CA  C.  CA  C.  CC  .C  CC  .C  
CC, CC, CC, .C, .C, .C, CA, CA, .A, .A, C., C., .., ..SAMPLE INPUT:4
..W.
..WW
WW..
...WSAMPLE OUTPUT:2304This satisfies the constraints for the first subtask described below.SCORING:Test cases 3-4 satisfy $N\le 10$ and there are at most ten unoccupied
squares.Test cases 5-9 satisfy $N\le 200$.Test cases 10-16 satisfy no additional constraints.Problem credits: Benjamin Qi

\section*{Sample Input}
\begin{verbatim}
2
..
..

4
..W.
..WW
WW..
...W
\end{verbatim}

\section*{Sample Output}
\begin{verbatim}
28

Here are all fourteen possibilities when sweet corn can grow at $(1,1)$.CC  .C  CA  CC  .C  CA  CA  C.  CA  C.  CC  .C  CC  .C  
CC, CC, CC, .C, .C, .C, CA, CA, .A, .A, C., C., .., ..SAMPLE INPUT:4
..W.
..WW
WW..
...WSAMPLE OUTPUT:2304This satisfies the constraints for the first subtask described below.SCORING:Test cases 3-4 satisfy $N\le 10$ and there are at most ten unoccupied
squares.Test cases 5-9 satisfy $N\le 200$.Test cases 10-16 satisfy no additional constraints.Problem credits: Benjamin Qi

CC  .C  CA  CC  .C  CA  CA  C.  CA  C.  CC  .C  CC  .C  
CC, CC, CC, .C, .C, .C, CA, CA, .A, .A, C., C., .., ..SAMPLE INPUT:4
..W.
..WW
WW..
...WSAMPLE OUTPUT:2304This satisfies the constraints for the first subtask described below.SCORING:Test cases 3-4 satisfy $N\le 10$ and there are at most ten unoccupied
squares.Test cases 5-9 satisfy $N\le 200$.Test cases 10-16 satisfy no additional constraints.Problem credits: Benjamin Qi

CC  .C  CA  CC  .C  CA  CA  C.  CA  C.  CC  .C  CC  .C  
CC, CC, CC, .C, .C, .C, CA, CA, .A, .A, C., C., .., ..

SAMPLE INPUT:4
..W.
..WW
WW..
...WSAMPLE OUTPUT:2304This satisfies the constraints for the first subtask described below.SCORING:Test cases 3-4 satisfy $N\le 10$ and there are at most ten unoccupied
squares.Test cases 5-9 satisfy $N\le 200$.Test cases 10-16 satisfy no additional constraints.Problem credits: Benjamin Qi

2304

This satisfies the constraints for the first subtask described below.SCORING:Test cases 3-4 satisfy $N\le 10$ and there are at most ten unoccupied
squares.Test cases 5-9 satisfy $N\le 200$.Test cases 10-16 satisfy no additional constraints.Problem credits: Benjamin Qi

SCORING:Test cases 3-4 satisfy $N\le 10$ and there are at most ten unoccupied
squares.Test cases 5-9 satisfy $N\le 200$.Test cases 10-16 satisfy no additional constraints.Problem credits: Benjamin Qi
\end{verbatim}

\section*{Solution}


\section*{Problem URL}
https://usaco.org/index.php?page=viewproblem2&cpid=1044

\section*{Source}
USACO OPEN20 Contest, Platinum Division, Problem ID: 1044

\end{document}
