\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\title{View problem}
\author{USACO Contest: DEC24 Contest - Gold Division}
\date{\today}

\begin{document}

\maketitle

\section*{Problem Statement}


Bessie the cow has $N$ ($1\le N\le 2\cdot 10^5$) jobs for you to potentially
complete. The $i$-th one, if you choose to complete it, must be started at or
before time $s_i$  and takes $t_i$ time to complete
($0\le s_i\le 10^{18}, 1\le t_i\le 10^{18}$).

What is the maximum number of jobs you can complete? Time starts at $0$, and
once you start a job you must work on it until it is complete, without starting
any other jobs in the meantime.

INPUT FORMAT (input arrives from the terminal / stdin):
The first line contains $T$, the number of independent test cases
($1\le T\le 10$). Each test case is formatted as follows.

The first line contains $N$.

Each of the next $N$ lines contains two integers $s_i$ and $t_i$. Row $i+1$ has
the details for the $i$th job.

It is guaranteed that the sum of $N$ over all test cases does not exceed
$3\cdot 10^5$.

OUTPUT FORMAT (print output to the terminal / stdout):
For each test case, the maximum number of jobs you can complete, on a new line.

SAMPLE INPUT:
3
2
1 4
1 2
2
2 3
1 2
3
1 4
2 3
1 2
SAMPLE OUTPUT: 
1
2
2

For the first test case, you can only complete one of the jobs. After completing
one job, it will then be time $2$ or later, so it is too late to start the other
job, which must be started at time $1$ or earlier.

For the second test case,  you can start the second job at time $0$ and finish
at time $2$,  then start the first job at time $2$ and finish at time $5$.

SCORING:
Inputs 2: Within the same test case, all $t_i$ are equal.Inputs 3-4: $N\le 2000$, $s_i, t_i\le 2000$Inputs 5-8: $N\le 2000$Inputs 9-16: No additional constraints.


Problem credits: Benjamin Qi



\section*{Input Format}
The first line contains $N$.Each of the next $N$ lines contains two integers $s_i$ and $t_i$. Row $i+1$ has
the details for the $i$th job.It is guaranteed that the sum of $N$ over all test cases does not exceed
$3\cdot 10^5$.

Each of the next $N$ lines contains two integers $s_i$ and $t_i$. Row $i+1$ has
the details for the $i$th job.It is guaranteed that the sum of $N$ over all test cases does not exceed
$3\cdot 10^5$.

It is guaranteed that the sum of $N$ over all test cases does not exceed
$3\cdot 10^5$.

OUTPUT FORMAT (print output to the terminal / stdout):For each test case, the maximum number of jobs you can complete, on a new line.SAMPLE INPUT:3
2
1 4
1 2
2
2 3
1 2
3
1 4
2 3
1 2SAMPLE OUTPUT:1
2
2For the first test case, you can only complete one of the jobs. After completing
one job, it will then be time $2$ or later, so it is too late to start the other
job, which must be started at time $1$ or earlier.For the second test case,  you can start the second job at time $0$ and finish
at time $2$,  then start the first job at time $2$ and finish at time $5$.SCORING:Inputs 2: Within the same test case, all $t_i$ are equal.Inputs 3-4: $N\le 2000$, $s_i, t_i\le 2000$Inputs 5-8: $N\le 2000$Inputs 9-16: No additional constraints.Problem credits: Benjamin Qi

\section*{Output Format}
SAMPLE INPUT:3
2
1 4
1 2
2
2 3
1 2
3
1 4
2 3
1 2SAMPLE OUTPUT:1
2
2For the first test case, you can only complete one of the jobs. After completing
one job, it will then be time $2$ or later, so it is too late to start the other
job, which must be started at time $1$ or earlier.For the second test case,  you can start the second job at time $0$ and finish
at time $2$,  then start the first job at time $2$ and finish at time $5$.SCORING:Inputs 2: Within the same test case, all $t_i$ are equal.Inputs 3-4: $N\le 2000$, $s_i, t_i\le 2000$Inputs 5-8: $N\le 2000$Inputs 9-16: No additional constraints.Problem credits: Benjamin Qi

\section*{Sample Input}
\begin{verbatim}
3
2
1 4
1 2
2
2 3
1 2
3
1 4
2 3
1 2
\end{verbatim}

\section*{Sample Output}
\begin{verbatim}
1
2
2

For the first test case, you can only complete one of the jobs. After completing
one job, it will then be time $2$ or later, so it is too late to start the other
job, which must be started at time $1$ or earlier.For the second test case,  you can start the second job at time $0$ and finish
at time $2$,  then start the first job at time $2$ and finish at time $5$.SCORING:Inputs 2: Within the same test case, all $t_i$ are equal.Inputs 3-4: $N\le 2000$, $s_i, t_i\le 2000$Inputs 5-8: $N\le 2000$Inputs 9-16: No additional constraints.Problem credits: Benjamin Qi

For the second test case,  you can start the second job at time $0$ and finish
at time $2$,  then start the first job at time $2$ and finish at time $5$.SCORING:Inputs 2: Within the same test case, all $t_i$ are equal.Inputs 3-4: $N\le 2000$, $s_i, t_i\le 2000$Inputs 5-8: $N\le 2000$Inputs 9-16: No additional constraints.Problem credits: Benjamin Qi

SCORING:Inputs 2: Within the same test case, all $t_i$ are equal.Inputs 3-4: $N\le 2000$, $s_i, t_i\le 2000$Inputs 5-8: $N\le 2000$Inputs 9-16: No additional constraints.Problem credits: Benjamin Qi
\end{verbatim}

\section*{Solution}


\section*{Problem URL}
https://usaco.org/index.php?page=viewproblem2&cpid=1451

\section*{Source}
USACO DEC24 Contest, Gold Division, Problem ID: 1451

\end{document}
