\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\title{View problem}
\author{USACO Contest: JAN21 Contest - Gold Division}
\date{\today}

\begin{document}

\maketitle

\section*{Problem Statement}

A little known fact about cows is that they have their own version of the
alphabet, the "cowphabet". It consists of the 26 letters 'a' through 'z', but
when a cow speaks the cowphabet, she lists these letters in a specific ordering
that might be different from the order 'abcdefghijklmnopqrstuvwxyz' we are used
to hearing.

To pass the time, Bessie's cousin Mildred has been humming the cowphabet over
and  over again, and Farmer Nhoj is curious how many times she's hummed it.

Given a lowercase string of letters that Farmer Nhoj has heard Mildred say,
compute the minimum number of times Mildred must have hummed the entire
cowphabet in order for Farmer Nhoj to have heard the given string. Farmer Nhoj
isn't always paying attention to what Mildred hums, and so he might have missed
some of the letters that Mildred has hummed. The string you are told consists of
just the letters that he remembers hearing.

Note: the time limit per test case on this problem is twice the default.

INPUT FORMAT (input arrives from the terminal / stdin):
The only line of input contains the string  of lowercase letters that Farmer
Nhoj heard Mildred say.  This string has length at least $1$ and at most $10^5$.

OUTPUT FORMAT (print output to the terminal / stdout):
Print the minimum number of times Mildred must have hummed the entire cowphabet.

SAMPLE INPUT:
mildredree
SAMPLE OUTPUT: 
3
Mildred must have hummed the cowphabet at least three times. It is possible for
Mildred to have only hummed the cowphabet three times if the cowphabet starts
with "mildre" and Farmer Nhoj heard the letters in uppercase as denoted below.


MILDREabcfghjknopqstuvwxyz
milDREabcfghjknopqstuvwxyz
mildrEabcfghjknopqstuvwxyz

SCORING:
In test cases 1-5, Farmer Nhoj only heard letters that appear in Mildred's
or Bessie's names.In test cases 6-16, Farmer Nhoj never heard any of the letters that appear
in Mildred's name.


Problem credits: Nick Wu and Brian Dean



\section*{Input Format}
OUTPUT FORMAT (print output to the terminal / stdout):Print the minimum number of times Mildred must have hummed the entire cowphabet.SAMPLE INPUT:mildredreeSAMPLE OUTPUT:3Mildred must have hummed the cowphabet at least three times. It is possible for
Mildred to have only hummed the cowphabet three times if the cowphabet starts
with "mildre" and Farmer Nhoj heard the letters in uppercase as denoted below.MILDREabcfghjknopqstuvwxyz
milDREabcfghjknopqstuvwxyz
mildrEabcfghjknopqstuvwxyzSCORING:In test cases 1-5, Farmer Nhoj only heard letters that appear in Mildred's
or Bessie's names.In test cases 6-16, Farmer Nhoj never heard any of the letters that appear
in Mildred's name.Problem credits: Nick Wu and Brian Dean

\section*{Output Format}
SAMPLE INPUT:mildredreeSAMPLE OUTPUT:3Mildred must have hummed the cowphabet at least three times. It is possible for
Mildred to have only hummed the cowphabet three times if the cowphabet starts
with "mildre" and Farmer Nhoj heard the letters in uppercase as denoted below.MILDREabcfghjknopqstuvwxyz
milDREabcfghjknopqstuvwxyz
mildrEabcfghjknopqstuvwxyzSCORING:In test cases 1-5, Farmer Nhoj only heard letters that appear in Mildred's
or Bessie's names.In test cases 6-16, Farmer Nhoj never heard any of the letters that appear
in Mildred's name.Problem credits: Nick Wu and Brian Dean

\section*{Sample Input}
\begin{verbatim}
mildredree
\end{verbatim}

\section*{Sample Output}
\begin{verbatim}
3

Mildred must have hummed the cowphabet at least three times. It is possible for
Mildred to have only hummed the cowphabet three times if the cowphabet starts
with "mildre" and Farmer Nhoj heard the letters in uppercase as denoted below.MILDREabcfghjknopqstuvwxyz
milDREabcfghjknopqstuvwxyz
mildrEabcfghjknopqstuvwxyzSCORING:In test cases 1-5, Farmer Nhoj only heard letters that appear in Mildred's
or Bessie's names.In test cases 6-16, Farmer Nhoj never heard any of the letters that appear
in Mildred's name.Problem credits: Nick Wu and Brian Dean

MILDREabcfghjknopqstuvwxyz
milDREabcfghjknopqstuvwxyz
mildrEabcfghjknopqstuvwxyzSCORING:In test cases 1-5, Farmer Nhoj only heard letters that appear in Mildred's
or Bessie's names.In test cases 6-16, Farmer Nhoj never heard any of the letters that appear
in Mildred's name.Problem credits: Nick Wu and Brian Dean

MILDREabcfghjknopqstuvwxyz
milDREabcfghjknopqstuvwxyz
mildrEabcfghjknopqstuvwxyz

SCORING:In test cases 1-5, Farmer Nhoj only heard letters that appear in Mildred's
or Bessie's names.In test cases 6-16, Farmer Nhoj never heard any of the letters that appear
in Mildred's name.Problem credits: Nick Wu and Brian Dean
\end{verbatim}

\section*{Solution}


\section*{Problem URL}
https://usaco.org/index.php?page=viewproblem2&cpid=1089

\section*{Source}
USACO JAN21 Contest, Gold Division, Problem ID: 1089

\end{document}
