\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\title{View problem}
\author{USACO Contest: OPEN19 Contest - Gold Division}
\date{\today}

\begin{document}

\maketitle

\section*{Problem Statement}

Farmer John wants to divide his $N$ cows $(N \leq 7500)$, conveniently 
numbered $1 \ldots N$, into $K$ non-empty
groups ($2 \leq K \leq N$) such that no two cows from two different groups can
interact with each other without walking some number of miles.  Cow $x$ and Cow $y$ (where
$1 \leq x < y \leq N$) are willing to walk
$(2019201913x + 2019201949y)\text{ mod } 2019201997$ miles to see each other. 

Given a division of the $N$ cows into $K$ non-empty groups, let $M$ be the
minimum of the number of miles any two cows in two different groups are willing
to walk to see each other.   To test the cows' devotion to each other, Farmer
John wants to optimally divide the $N$ cows into $K$ groups such that $M$ is as
large as possible. 

The memory limit for this problem is set to 512MB, above
the usual 256MB limit.

INPUT FORMAT (file walk.in):
The input is just one line, containing $N$ and $K$, separated by a space.

OUTPUT FORMAT (file walk.out):
Print out $M$ in an optimal solution. 
SAMPLE INPUT:
3 2
SAMPLE OUTPUT: 
2019201769

In this example, Cow 1 and Cow 2 are willing to walk 2019201817 miles to see
each other.  Cow 2 and Cow 3 are willing to walk 2019201685 miles. And Cow 1 and
Cow 3 are  willing to walk 2019201769 miles. Thus, by grouping the cows such
that  1 is by herself and 2 and 3 are grouped together,
$M = \min(2019201817,2019201769) = 2019201769$ (which is the best we can do
here).


Problem credits: Brian Dean



\section*{Input Format}
OUTPUT FORMAT (file walk.out):Print out $M$ in an optimal solution.SAMPLE INPUT:3 2SAMPLE OUTPUT:2019201769In this example, Cow 1 and Cow 2 are willing to walk 2019201817 miles to see
each other.  Cow 2 and Cow 3 are willing to walk 2019201685 miles. And Cow 1 and
Cow 3 are  willing to walk 2019201769 miles. Thus, by grouping the cows such
that  1 is by herself and 2 and 3 are grouped together,
$M = \min(2019201817,2019201769) = 2019201769$ (which is the best we can do
here).Problem credits: Brian Dean

\section*{Output Format}
SAMPLE INPUT:3 2SAMPLE OUTPUT:2019201769In this example, Cow 1 and Cow 2 are willing to walk 2019201817 miles to see
each other.  Cow 2 and Cow 3 are willing to walk 2019201685 miles. And Cow 1 and
Cow 3 are  willing to walk 2019201769 miles. Thus, by grouping the cows such
that  1 is by herself and 2 and 3 are grouped together,
$M = \min(2019201817,2019201769) = 2019201769$ (which is the best we can do
here).Problem credits: Brian Dean

\section*{Sample Input}
\begin{verbatim}
3 2
\end{verbatim}

\section*{Sample Output}
\begin{verbatim}
2019201769

In this example, Cow 1 and Cow 2 are willing to walk 2019201817 miles to see
each other.  Cow 2 and Cow 3 are willing to walk 2019201685 miles. And Cow 1 and
Cow 3 are  willing to walk 2019201769 miles. Thus, by grouping the cows such
that  1 is by herself and 2 and 3 are grouped together,
$M = \min(2019201817,2019201769) = 2019201769$ (which is the best we can do
here).Problem credits: Brian Dean

Problem credits: Brian Dean

Problem credits: Brian Dean
\end{verbatim}

\section*{Solution}


\section*{Problem URL}
https://usaco.org/index.php?page=viewproblem2&cpid=946

\section*{Source}
USACO OPEN19 Contest, Gold Division, Problem ID: 946

\end{document}
