\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\title{View problem}
\author{USACO Contest: OPEN20 Contest - Gold Division}
\date{\today}

\begin{document}

\maketitle

\section*{Problem Statement}

Farmer John has come up with a new morning exercise routine for the cows
(again)!

As before, Farmer John's $N$ cows ($1\le N\le 10^4$) are standing in a line. 
The $i$-th cow from the left has label $i$ for each $1\le i\le N$. He tells them
to repeat the following step until the cows are in the same order as when they
started.

Given a permutation $A$ of length $N$, the cows change their order such that
the $i$-th cow from the left before the change is $A_i$-th from the left after
the change. 
For example, if $A=(1,2,3,4,5)$ then the cows perform one step. If 
$A=(2,3,1,5,4)$, then the cows perform six steps. The order of the cows from
left to right after each step is as follows:

0 steps: $(1,2,3,4,5)$1 step: $(3,1,2,5,4)$2 steps: $(2,3,1,4,5)$3 steps: $(1,2,3,5,4)$4 steps: $(3,1,2,4,5)$5 steps: $(2,3,1,5,4)$6 steps: $(1,2,3,4,5)$
Find the sum of all positive integers $K$ such that there exists a permutation
of length $N$ that requires the cows to take exactly $K$ steps. 

As this number may be very large, output the answer modulo $M$
($10^8\le M\le 10^9+7$, $M$ is prime).

INPUT FORMAT (file exercise.in):
The first line contains $N$ and $M$.

OUTPUT FORMAT (file exercise.out):
A single integer.

SAMPLE INPUT:
5 1000000007
SAMPLE OUTPUT: 
21

There exist permutations that cause the cows to take $1$, $2$, $3$, $4$, $5$,
and $6$ steps. Thus, the answer is $1+2+3+4+5+6=21$.

SCORING:
Test cases 2-5 satisfy $N\le 10^2$.Test cases 6-10 satisfy no additional constraints.


Problem credits: Benjamin Qi



\section*{Input Format}
OUTPUT FORMAT (file exercise.out):A single integer.SAMPLE INPUT:5 1000000007SAMPLE OUTPUT:21There exist permutations that cause the cows to take $1$, $2$, $3$, $4$, $5$,
and $6$ steps. Thus, the answer is $1+2+3+4+5+6=21$.SCORING:Test cases 2-5 satisfy $N\le 10^2$.Test cases 6-10 satisfy no additional constraints.Problem credits: Benjamin Qi

\section*{Output Format}
SAMPLE INPUT:5 1000000007SAMPLE OUTPUT:21There exist permutations that cause the cows to take $1$, $2$, $3$, $4$, $5$,
and $6$ steps. Thus, the answer is $1+2+3+4+5+6=21$.SCORING:Test cases 2-5 satisfy $N\le 10^2$.Test cases 6-10 satisfy no additional constraints.Problem credits: Benjamin Qi

\section*{Sample Input}
\begin{verbatim}
5 1000000007
\end{verbatim}

\section*{Sample Output}
\begin{verbatim}
21

There exist permutations that cause the cows to take $1$, $2$, $3$, $4$, $5$,
and $6$ steps. Thus, the answer is $1+2+3+4+5+6=21$.SCORING:Test cases 2-5 satisfy $N\le 10^2$.Test cases 6-10 satisfy no additional constraints.Problem credits: Benjamin Qi

SCORING:Test cases 2-5 satisfy $N\le 10^2$.Test cases 6-10 satisfy no additional constraints.Problem credits: Benjamin Qi
\end{verbatim}

\section*{Solution}


\section*{Problem URL}
https://usaco.org/index.php?page=viewproblem2&cpid=1043

\section*{Source}
USACO OPEN20 Contest, Gold Division, Problem ID: 1043

\end{document}
